\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-30 latex/article_vol2.tex
Halfway done with TeX fixes

@@

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\begin{center}    
\begin{tikzpicture}[node distance = 2cm, auto,thick,scale=0.75, every node/.style={transform shape}]
    % Place nodes
    \node [block] (init) {Get next variable and run pre-checks};
    \node [cloud, above of=init] (input) {Input \texttt{data.frame} or \texttt{tibble}};
%    \node [cloud, right of=init] (system) {system};
    \node [decision, right of=init, node distance=4cm] (precheck) {Is variable suitable for inclusion};
    \node [block, right of=precheck, node distance=4cm] (summarize)
    {Run \texttt{summarize()} to produce summary table};
    \node [block, below of=summarize, node distance=3cm] (visualize)
    {Run \texttt{visualize()} to plot variable};
    \node [block, below of=visualize, node distance=2.5cm] (check)
    {Call \texttt{check()} to run error checks};
    \node [decision, below of=check, node distance=2.7cm] (done) {More
      variables?};
    \node [block, right of=done, node distance=3.5cm] (stop) {Write
      \proglang{R} markdown file};
    \node [cloud, below of=stop, node distance=3.5cm] (render) {Render
      markdown and possiby open};
    % Draw edges
    \path [line] (summarize) -- (visualize);
    \path [line] (visualize) -- (check);
    \path [line] (check) -- (done);
    \path [line] (done.south) -- +(0,-10pt) -| node [near start] {yes} (init);
%    \path [line] (identify) -- (evaluate);
%    \path [line] (evaluate) -- (decide);
%    \path [line] (init) -| node [near start] {yes} (precheck);
    \path [line] (init) -- (precheck);
    \path [line] (precheck) -- node [near start] {yes} (summarize);
    \path [line] (precheck) |- node [near start] {no} (done);
    \path [line] (done) -- node [near start] {no} (stop);
%    \path [line] (update) |- (identify);
%    \path [line] (decide) -- node {no}(stop);
    \path [line,dashed] (input) -- (init);
%    \path [line,dashed] (system) -- (init);
%    \path [line,dashed] (system) |- (evaluate);
\end{tikzpicture}
\end{center}

@@

\begin{table}[ht]
\scriptsize
\begin{tabular}{L{0.2\linewidth}L{0.2\linewidth}L{0.2\linewidth}L{0.2\linewidth}}
& \R{summaryFunction} & \R{visualFunction} & \R{checkFunction} \\
\hline
Input (required) & \R{v} - a variable vector \newline \R{...}  &  \R{v} - a variable vector \newline \R{vnam} - the variable name (as character string) \newline \R{doEval} - a logical (\R{TRUE}/\R{FALSE}) controlling the output type of the function & \R{v} - a variable vector \newline \R{nMax} - an integer (or \R{Inf}), controlling how many problematic values are printed, if relevant \newline \R{...}  \\
Input (optional) &  \R{maxDecimals} - number of decimals printed in outputted numerical values.  & - &  \R{maxDecimals}  - number of decimals printed in outputted numerical values.  \\
Purpose & Describe some aspect of the variable, e.g. a central value, its dispersion or level of missingness. & Produce a distribution plot. & Check a variable for a specific issue and, if relevant, identify the values in the variable that cause the issue. \\
Output (required) & A list with entries: \newline \R{\$feature} - a label for the summary value (as character string); \newline \R{\$result} - the result of the summary (as character string) & A character string with \R{R} code for producing a plot. This code should be standalone, i.e. should include the data if necessary. & A list with entries: \newline \R{\$problem} - a logical identifying whether an issue was found; \newline \R{\$message} - a character string (possibly empty) decribing the issue that was found, properly escaped and ready for use in \R{rmarkdown} \\
Output (recommended) & A \R{summaryResult} object, i.e. an attributed list with entries \R{\$feature}, \R{\$result} and \R{\$value}, the latter being the values from \R{\$result} in their original format). & \begin{tabular}{p{0.4\linewidth} | p{0.4\linewidth}} If \R{doEval} is \R{TRUE}: \newline A plot that will be opened by the graphic device in \R{R}. & If \R{doEval} is \R{FALSE}: \newline   A text string with \R{R} code, as described above. \end{tabular} & A \R{checkResult} object, i.e. an attributed list with entries \R{\$problem}, \R{\$message} and \R{\$problemValues}, the latter being either \R{NULL} or the problem causing values, as they were found in \R{v}, whichever is relevant. \\
Tools available for producing the function & \R{summaryResult()} & - & \R{messageGenerator()} \newline \R{checkResult()} 
\end{tabular}
\caption{Reference information for creating new functions to be used
  as part of the summarize-, visualize-, and check steps. The three
  columns correspond to each of the three function types. \hl{I think the formatting here is still sort of chaotic. Maybe include horizontal lines everywhere? Is it allowed in JSS? It's impossible to read what's in which row right now.}}
\label{table.functionTypes}
\end{table}

@@

>>>>

\renewcommand\topfraction{.9}
\renewcommand\textfraction{.1}
\renewcommand{\floatpagefraction}{.6}

\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

@@

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

@@

\begin{center}    
\begin{tikzpicture}[node distance = 2cm, auto,thick,scale=0.75, every node/.style={transform shape}]
    % Place nodes
    \node [block] (init) {Get next variable and run pre-checks};
    \node [cloud, above of=init] (input) {Input \texttt{data.frame} or \texttt{tibble}};
%    \node [cloud, right of=init] (system) {system};
    \node [decision, right of=init, node distance=4cm] (precheck) {Is variable suitable for inclusion};
    \node [block, right of=precheck, node distance=4cm] (summarize)
    {Run \texttt{summarize()} to produce summary table};
    \node [block, below of=summarize, node distance=3cm] (visualize)
    {Run \texttt{visualize()} to plot variable};
    \node [block, below of=visualize, node distance=2.5cm] (check)
    {Call \texttt{check()} to run error checks};
    \node [decision, below of=check, node distance=2.7cm] (done) {More
      variables?};
    \node [block, right of=done, node distance=3.5cm] (stop) {Write
      \proglang{R} markdown file};
    \node [cloud, below of=stop, node distance=3.5cm] (render) {Render
      markdown and possiby open};
    % Draw edges
    \path [line] (summarize) -- (visualize);
    \path [line] (visualize) -- (check);
    \path [line] (check) -- (done);
    \path [line] (done.south) -- +(0,-10pt) -| node [near start] {yes} (init);
%    \path [line] (identify) -- (evaluate);
%    \path [line] (evaluate) -- (decide);
%    \path [line] (init) -| node [near start] {yes} (precheck);
    \path [line] (init) -- (precheck);
    \path [line] (precheck) -- node [near start] {yes} (summarize);
    \path [line] (precheck) |- node [near start] {no} (done);
    \path [line] (done) -- node [near start] {no} (stop);
%    \path [line] (update) |- (identify);
%    \path [line] (decide) -- node {no}(stop);
    \path [line,dashed] (input) -- (init);
    \path [line] (stop) -- (render);
%    \path [line,dashed] (system) -- (init);
%    \path [line,dashed] (system) |- (evaluate);
\end{tikzpicture}
\end{center}

@@

@@

\begin{table}[htbp]
\footnotesize
\bgroup
\def\arraystretch{1.8}% 
\begin{tabular}{L{0.2\linewidth}L{0.2\linewidth}L{0.2\linewidth}L{0.2\linewidth}}
& \R{summaryFunction} & \R{visualFunction} & \R{checkFunction} \\
\hline
\vspace{0pt} Input (required) & \R{v} - a variable vector \newline \R{...}  &  \R{v} - a variable vector \newline \R{vnam} - the variable name (as character string) \newline \R{doEval} - a logical (\R{TRUE}/\R{FALSE}) controlling the output type of the function & \R{v} - a variable vector \newline \R{nMax} - an integer (or \R{Inf}), controlling how many problematic values are printed, if relevant \newline \R{...}  \\
Input (optional) &  \R{maxDecimals} - number of decimals printed in outputted numerical values.  & - &  \R{maxDecimals}  - number of decimals printed in outputted numerical values.  \\
Purpose & Describe some aspect of the variable, e.g. a central value, its dispersion or level of missingness. & Produce a distribution plot. & Check a variable for a specific issue and, if relevant, identify the values in the variable that cause the issue. \\
Output (required) & A list with entries: \newline \R{\$feature} - a label for the summary value (as character string); \newline \R{\$result} - the result of the summary (as character string) & A character string with \R{R} code for producing a plot. This code should be standalone, i.e. should include the data if necessary. & A list with entries: \newline \R{\$problem} - a logical identifying whether an issue was found; \newline \R{\$message} - a character string (possibly empty) decribing the issue that was found, properly escaped and ready for use in \R{rmarkdown} \\
Output (recommended) & A \R{summaryResult} object, i.e. an attributed list with entries \R{\$feature}, \R{\$result} and \R{\$value}, the latter being the values from \R{\$result} in their original format). & \bgroup
\def\arraystretch{1.8}% 
\hspace*{-.2cm}\begin{tabular}[t]{p{0.45\linewidth} | p{0.45\linewidth}} \vspace*{-.9cm}If \R{doEval} is \R{TRUE}: \newline A plot that is opened by the graphic device in \R{R}. & \vspace*{-.9cm}If \R{doEval} is \R{FALSE}: \newline   A text string with \R{R} code, as described above. \end{tabular} \egroup  & A \R{checkResult} object, i.e. an attributed list with entries \R{\$problem}, \R{\$message} and \R{\$problemValues}, the latter being either \R{NULL} or the problem causing values, as they were found in \R{v}, whichever is relevant. \\
Tools available for producing the function & \R{summaryResult()} & --- & \R{messageGenerator()} \newline \R{checkResult()} 
\end{tabular}
\egroup
\caption{Reference information for creating new functions to be used
  as part of the \mbox{summarize-,} visualize-, and check steps. The three
  columns correspond to each of the three function types. %\hl{I think the formatting here is still sort of chaotic. Maybe include horizontal lines everywhere? Is it allowed in JSS? It's impossible to read what's in which row right now.}
}
\label{table.functionTypes}
\end{table}
